Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/suppl_material.tex

>>>>

\begin{table*}
	\small
	\centering
\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	          vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
	\midrule
	  train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
	  car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
	  plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
	  airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
	  motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
	  truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
	 boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
	  jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
	  aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
	  van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
	\bottomrule
\end{tabular}
	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset1}}
\end{table*}
